### 2022-09-15 main/chapter_searches.tex
add note on estimating p-values

\subsection{Like-lihood modelling}

\TODO{
on ``likelihood'' models ---
we are instructed to pretend that these are likelihoods on auxiliary data
TODO cite.
One is free to engage in such doublethink~\cite{orwell1949nnineteen},
% just as one is free to proclaim that $2 + 2 = 5$
but the fact remains that many constraints do not correspond to predictions of
auxiliary data so are not likelihoods: examples include
scale variations,
theoretical cross-section uncertainties,
non-closure uncertainties (which cover differences between estimates).
simulated sample comparisons,
statistical errors on weighted simulations,
extrapolation uncertainties,
and
all uncertainties on supersymmetric signal yields
(for which we have yet no data).
energy based modelling ---
I know of no tangible benefit from pretending that something is a likelihood
when it is not.
}

>>>>

A great benefit to these modified maximum likelihood ratios is that their
sampling distributions have known approximations in asymptotic (Gaussian)
limits, which assign \pvalues\ through well-behaved analytic
expressions~\cite{Cowan:2010js}.
Without such formulae, the remaining practical approach to estimating
\pvalues\ is to generate Monte Carlo simulations of alternative data.
Such simulations can be computationally expensive, and even hard to define for
``likelihood'' models that blur the line between actual data and
auxiliary model parameters.

\subsection{Like-lihood modelling}
\TODO{
on ``likelihood'' models ---
we are instructed to pretend that these are likelihoods on auxiliary data
TODO cite.
One is free to engage in such doublethink~\cite{orwell1949nnineteen},
% just as one is free to proclaim that $2 + 2 = 5$
but the fact remains that many constraints do not correspond to predictions of
auxiliary data so are not likelihoods: examples include
scale variations,
theoretical cross-section uncertainties,
non-closure uncertainties (which cover differences between estimates).
simulated sample comparisons,
statistical errors on weighted simulations,
extrapolation uncertainties,
and
all uncertainties on supersymmetric signal yields
(for which we have yet no data).
energy based modelling ---
I know of no tangible benefit from pretending that something is a likelihood
when it is not.
}
